Measuring Subgroup Preferences in Conjoint Experiments

### 2018-02-20 manuscript.tex
initial commit

\documentclass[a4paper,12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{times}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{setspace}
\renewcommand{\thefigure}{S\arabic{figure}}
\usepackage[normalem]{ulem}
\usepackage{sectsty}
\subsectionfont{\normalfont\large\underline}

\title{Measuring Subgroup Preferences in Conjoint Experiments}
\author{Sara Hobolt, Thomas J. Leeper, and James Tilley}

\begin{document}

@@

<<r hidden, eval=FALSE, echo=FALSE, results="hide">>=
# setwd("c:/users/thomas/dropbox/brexit identity/papers/subgroupanalysis")
# knitr::knit2pdf("manuscript.Rnw")
@

<<r knitr_options, echo=FALSE, results="hide">>=
knitr::opts_chunk$set(cache = TRUE, echo=FALSE, results="hold", warning=FALSE)
options(scipen = 10)
@

@@

<<r setup>>=
library("ggplot2")
requireNamespace("ggstance")
library("cregg")
@

<<r data>>=
data(hainmueller)
hainmueller$ethnocentrism_split <- ifelse(is.na(hainmueller$ethnocentrism), NA_real_, ifelse(hainmueller$ethnocentrism > 10, 1, 0))
hainmueller$ethnocentrism_split <- factor(hainmueller$ethnocentrism_split, levels = c(0,1), labels = c("low", "high"))
@

@@

<<r hainmueller_immigration, dependson=c("data"), fig.height=10, fig.width=8>>=
plot(
  cj(
   hainmueller, 
   ChosenImmigrant ~ Gender + Education + LanguageSkills + CountryOfOrigin + Job + JobExperience + JobPlans + ReasonForApplication + PriorEntry,
   id = ~ CaseID
  )
)
@

@@

<<r functions>>=
amces_by_reference <- function(data, variable, formula) {
    # get levels
    levs <- levels(data[[variable]])

    # loop over levels
    out <- list()
    for (i in seq_along(levs)) {
        data[[variable]] <- relevel(data[[variable]], levs[i])
        out[[i]] <- cj(data, formula, id = ~ CaseID)
        out[[i]][["ref_category"]] <- levs[i]
    }

    # return value
    out <- do.call("rbind", out)
    out[["ref_category"]] <- factor(out[["ref_category"]], levels = levs)
    class(out) <- c("cj_amce", "data.frame")
    out
}
@

@@

<<r reference_category, dependson=c("data"), fig.width=8, fig.height=5>>=
x <- amces_by_reference(hainmueller, "CountryOfOrigin", ChosenImmigrant ~ CountryOfOrigin)

ggplot(x, aes(x = estimate, y = level, group = ref_category, colour = level)) +
  geom_vline(xintercept = 0, colour = "gray") +
  geom_point(position = ggstance::position_dodgev(height = 0.75)) +
  geom_errorbarh(aes(xmin = lower, xmax = upper),  
                 size = 0.2, height = 0,
                 position = ggstance::position_dodgev(height = 0.75)) + 
  scale_colour_discrete(guide = ggplot2::guide_legend(title = "Reference Category")) +
  scale_x_continuous(limits = c(-.3,.3), oob = scales::rescale_none) +
  ylab("") +
  xlab("Estimated AMCE") + 
  theme_minimal() + 
      ggplot2::theme(
        legend.position = "bottom",
        panel.grid.major = ggplot2::element_blank(),
        panel.grid.minor = ggplot2::element_blank()
      )
@

<<r marginal_means, fig.width=8, fig.height=5>>=
plot(mm(hainmueller, ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID), vline = 0.5, xlim = c(0,1))
@

@@

<<r subgroup_results_amce, dependson=c("data"), fig.width=8, fig.height=5>>=
by_split <- lapply(c("low","high"), function(x) {
    out <- cj(na.omit(hainmueller[hainmueller$ethnocentrism_split == x,]), ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID, estimate = "amce")
    out$ethnocentrism_split <- x
    out
})
x <- do.call("rbind", by_split)

ggplot(x, aes(x = estimate, y = level, group = ethnocentrism_split, colour = ethnocentrism_split)) +
  geom_vline(xintercept = 0, colour = "gray") +
  geom_point(position = ggstance::position_dodgev(height = 0.75)) +
  geom_errorbarh(aes(xmin = lower, xmax = upper),  
                 size = 0.2, height = 0,
                 position = ggstance::position_dodgev(height = 0.75)) + 
  scale_colour_discrete(guide = ggplot2::guide_legend(title = "Ethnocentrism")) +
  scale_x_continuous(limits = c(-.3,.3), oob = scales::rescale_none) +
  ylab("") +
  xlab("Estimated AMCE") + 
  theme_minimal() + 
      ggplot2::theme(
        legend.position = "bottom",
        panel.grid.major = ggplot2::element_blank(),
        panel.grid.minor = ggplot2::element_blank()
      )
@

<<r subgroup_marginal_means, dependson=c("data"), fig.width=8, fig.height=5>>=
plot(cj(hainmueller, ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID, estimate = "mm", by = ~ethnocentrism_split), vline = 0.5, group = "ethnocentrism_split")
@

@@

<<r subgroup_results_mm, dependson=c("data"), fig.width=10, fig.height=10>>=
# difference in marginal means
by_split_mm <- lapply(levels(hainmueller$ethnocentrism_split), function(x) {
    out <- cj(na.omit(hainmueller[hainmueller$ethnocentrism_split == x,]), ChosenImmigrant ~ CountryOfOrigin, id = ~ CaseID, estimate = "mm")
    out$ethnocentrism_split <- x
    out
})
x_mm <- merge(by_split_mm[[1]], by_split_mm[[2]], by = c("level"), suffixes = c(".low", ".high"))
## difference
x_mm[["diff"]] <- x_mm[["estimate.high"]] - x_mm[["estimate.low"]]
## standard error of difference
x_mm[["diff_se"]] <- sqrt(x_mm[["std.error.high"]]^2 + x_mm[["std.error.low"]]^2)
x_mm[["ref_category"]] <- "Marginal Mean"

# difference in AMCEs
by_split_amce <- lapply(levels(hainmueller$ethnocentrism_split), function(x) {
    out <- amces_by_reference(na.omit(hainmueller[hainmueller$ethnocentrism_split == x,]), "CountryOfOrigin", ChosenImmigrant ~ CountryOfOrigin)
    out$ethnocentrism_split <- x
    out
})
x_amce <- merge(by_split_amce[[1]], by_split_amce[[2]], by = c("level", "ref_category"), suffixes = c(".low", ".high"))
## difference
x_amce[["diff"]] <- x_amce[["estimate.high"]] - x_amce[["estimate.low"]]
## standard error of difference
x_amce[["diff_se"]] <- sqrt(x_amce[["std.error.high"]]^2 + x_amce[["std.error.low"]]^2)

x_merged <- rbind(x_mm[c("level", "diff", "diff_se", "ref_category")], x_amce[c("level", "diff", "diff_se", "ref_category")])
x_merged[["ref_category"]] <- factor(x_merged[["ref_category"]], levels = c("Marginal Mean", levels(x_amce[["ref_category"]])))
x_merged[["is_mm"]] <- ifelse(x_merged[["ref_category"]] == "Marginal Mean", "Difference in MMs", "Difference in AMCEs")

ggplot(x_merged, aes(x = diff, y = level, group = ref_category, colour = is_mm, shape = is_mm)) +
  geom_vline(xintercept = 0, colour = "gray") +
  geom_point(aes(shape = is_mm), position = ggstance::position_dodgev(height = 0.75)) +
  scale_shape_manual(values = c(16,15), guide = FALSE) + 
  geom_errorbarh(aes(xmin = diff - diff_se, xmax = diff + diff_se),  
                 size = 0.2, height = 0,
                 position = ggstance::position_dodgev(height = 0.75)) + 
  #scale_colour_discrete(guide = ggplot2::guide_legend(title = "Reference Category")) +
  scale_colour_manual(values = c("gray", "red"), guide = ggplot2::guide_legend(title = "Estimate Type")) +
  scale_x_continuous(oob = scales::rescale_none) +
  ylab("") +
  xlab("Estimated Difference") + 
  theme_minimal() + 
      ggplot2::theme(
        legend.position = "right",
        panel.grid.major = ggplot2::element_blank(),
        panel.grid.minor = ggplot2::element_blank()
      )
@

>>>>

\documentclass[a4paper,12pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{times}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{setspace}
\renewcommand{\thefigure}{S\arabic{figure}}
\usepackage[normalem]{ulem}
\usepackage{sectsty}
\subsectionfont{\normalfont\large\underline}

\title{Measuring Subgroup Preferences in Conjoint Experiments}
\author{Sara Hobolt, Thomas J. Leeper, and James Tilley}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

@@

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Loading required namespace: ggstance}}\end{kframe}
\includegraphics[width=\maxwidth]{figure/r_hainmueller_immigration-1}

\end{knitrout}

@@

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/r_reference_category-1}

\end{knitrout}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/r_marginal_means-1}

\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/r_subgroup_results_amce-1}

\end{knitrout}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/r_subgroup_marginal_means-1}

\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/r_subgroup_results_mm-1}

\end{knitrout}
